Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2018-12-20 tex/WW4C_VHzQ.tex
tex tables re-arrange
tex/WW4C_VHzQ update

Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.  
\input{THE_TABLE_v0pnt96_TOP10_betterformat}

@@

>>>>

Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.

\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}

%\input{table_tex/THE_TABLE_v0pnt96_TOP10_redshifts}
%\input{table_tex/THE_TABLE_v0pnt96_TOP10_NIR}
%\input{table_tex/THE_TABLE_v0pnt96_TOP10_MIR}

@@

    \subsubsection{Salient details of WSA and VSA}. 
    %% N.B.!!!    WFAU archives more than just the NIR Surveys -- it archives *all* the WFCAM and VISTA programmes!!
    In this study, we are not just quering the WSA or VSA data tables. 
    We are taking a list of objects (positions) are performing matched aperature (``forced'') photometry on the NIR imaging data. 
    As such, we generate a set of tables that are different in subtle ways to the regular ``Detection'' tables.

    The two most important tables for our needs are the {\tt [w/v]serv1000MapRemeasurement} and {\tt [w/v]serv1000MapRemeasAver}.

    Full documentation can be found at the \href{http://wsa.roe.ac.uk/www/wsa_browser.html}{WSA Schema Browser} 
and the \href{http://horus.roe.ac.uk/vsa/www/vsa_browser.html}{VSA Schema Browser}.
